Windowed Developer Topic Analysis

### 2009-03-19 lda-paper.tex
More changes to stuff

\subsection{Compare to topics over entire development}
\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{maxdb7500-everything-by-month}
  \caption{MaxDB 7.500 Topics Analyzed with Static Topic Analysis, 20
    topics over the entire development history of MaxDB 7.500. Each
    box indicates the number of documents matching that topic in that
    month.}
  \label{fig:statictopics}
\end{figure}

>>>>

\subsection{Compare to topics over entire development}

The previous work which leverage LSI or LDA usually extracted a
certain number of topics and tracked them over time. This meant a
static set of topics was tracked across the whole development history
of a project. Thus we really had 20 trends.

We attempted the same kind of analysis, as shown in
Figure~\ref{fig:statictopics} we extracted 20 topics and then plotted
the number of messages per month which related to that topic. What we
found was that often one topic would dominate the results, while
messages related to other topics didn't appear that often.

This technique seems useful if the 20 extracted topics are relevant
and useful, that said one weakness of this approach is that documents
for a topic might only occur in one time window, yet we're tracking
messages that could be related to it over the entire lifetime of the
project.

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{maxdb7500-everything-by-month}
  \caption{MaxDB 7.500 Topics Analyzed with Static Topic Analysis, 20
    topics over the entire development history of MaxDB 7.500. Each
    box indicates the number of documents matching that topic in that
    month.}
  \label{fig:statictopics}
\end{figure}
